\speculake: Hiding Malware in Speculative Execution

### 2018-05-09 paper/related-work.tex
typos

As another example, Bangert~\textit{et al.} demonstrate that a turing complete weird machine 
can be constructed using the page fault handling mechanism in Intel's
IA32 architecture~\cite{bangert2013page}.

@@

% Discovery & Followup
Given the numerous directions that were being investigated in reverse engineering 
Intel processors, multiple teams discovered the Spectre vulnerabilities concurrently including 
the teams associated with Kocher \textit{et al.}~\cite{spectre}, the Project Zero team 
at Google~\cite{project_zero},and various others~\cite{evtyushkin2018branchscope,maisuradze2018speculose}. 
%These works propose multiple variants making use of branch prediction.
Follow 
up work on speculative execution side channels has also demonstrated
web-based vulnerabilites~\cite{genkin2018drive} as well as hardware isolation  
leaks in Intel's SGX~\cite{spectre_sgx}. At the time of writing multiple sources
have claimed new speculative execution related exploits termed \textit{Spectre-NG}
have been reported to Intel and assigned CVE numbers, though details are
not yet available~\cite{spectre_ng_gossip}.
%We have no details
%on content, though Intel has labeled four as critical and another four 
%as intermediate security flaws~\cite{spectre_ng_gossip}.

>>>>

As another example, Bangert~\textit{et al.} demonstrate that a Turing complete
weird machine can be constructed using the page fault handling mechanism in
Intel's IA32 architecture~\cite{bangert2013page}.

@@

% Discovery & Followup
Given the numerous directions that were being investigated in reverse
engineering Intel processors, multiple teams discovered the Spectre
vulnerabilities concurrently including the teams associated with Kocher
\textit{et al.}~\cite{spectre}, the Project Zero team at
Google~\cite{project_zero}, and various
others~\cite{evtyushkin2018branchscope,maisuradze2018speculose}. 
%These works propose multiple variants making use of branch prediction.
Follow 
up work on speculative execution side channels has also demonstrated
web-based vulnerabilites~\cite{genkin2018drive} as well as hardware isolation  
leaks in Intel's SGX~\cite{spectre_sgx}. At the time of writing multiple sources
have claimed new speculative execution related exploits termed \textit{Spectre-NG}
have been reported to Intel and assigned CVE numbers, though details are
not yet available~\cite{spectre_ng_gossip}.
%We have no details
%on content, though Intel has labeled four as critical and another four 
%as intermediate security flaws~\cite{spectre_ng_gossip}.
